New lower bounds for Schur and weak Schur numbers

### 2021-09-23 article/article.tex

We would first like to thank our professors, Joanna Tomasik and Arpad Rimmel, who guided and advised
us during the whole research and writing. We also would like to address warm thanks
to Fred Rowley who kindly answered our many questions and with who it was a pleasure to exchange. 
Last but not least, we would like to thank Marijn Heule for providing the backdoors used in the computation of the 
new lower bound for \(\WS(6)\).

>>>>

\qquad We would first like to thank our school CentraleSupélec and its Research Pole 005 led by Joanna Tomasik allowing us to
make this project in our studies. We also would like to address warm thanks to Fred Rowley who kindly answered our many questions
and with who it was a pleasure to exchange. Last but not least, we would like to thank Marijn Heule for providing the backdoors
used in the computation of the new lower bound for \(\WS(6)\).

### 2021-09-23 article/weakschur.tex

\qquad We produced WS-templates using a SAT solver, hence providing lower bound on \(WS^+\) and inequalities
of the type \(WS(n+k) \geqslant a S(n) + b\). We sought templates providing the greatest value of \((a, b)\) (in the 
lexicographic order). Details concerning the encoding as a SAT problem can be found in \cite{Heule2017}.

@@

\subsection{Another approach: \(\WS(6) \geqslant 646\)}
\qquad The weak Schur partitions obtained with WS-templates have an extremely regular structure. Therefore, one may 
expect to find larger partitions by allowing more freedom in the structure of the partition while still preserving a structure 
somewhat close to a template-based partition thus reducing the search space to a manageable size.

@@

\qquad We started by giving a new construction which can be seen as an equivalent for weakly sum-free partitions of Abott
and Hanson's construction for sum-free partitions. We then generalized this construction by introducing WS-templates. This
allows us to find new lower bounds and new inequalities for weak Schur numbers. One may notice the significant gap
between the former lower bounds for weak Schur numbers obtained by conducting a computer search and the new lower bounds
obtained with WS-templates. We reckon better WS-templates with \(n \geqslant 5\) colors can be found by making different assumptions 
and using a different method (Monte-Carlo methods for instance).

>>>>

We produced WS-templates using a SAT solver, hence providing lower bound on \(WS^+\) and inequalities
of the type \(WS(n+k) \geqslant a S(n) + b\). We sought templates providing the greatest value of \((a, b)\) (in the 
lexicographic order). Details concerning the encoding as a SAT problem can be found in \cite{Heule2017}.

@@

\subsection{Another approach: \(\WS(6) \geqslant 646\)}

The weak Schur partitions obtained with WS-templates have an extremely regular structure. Therefore, one may 
expect to find larger partitions by allowing more freedom in the structure of the partition while still preserving a structure 
somewhat close to a template-based partition thus reducing the search space to a manageable size.

@@

We started by giving a new construction which can be seen as an equivalent for weakly sum-free partitions of Abott
and Hanson's construction for sum-free partitions. We then generalized this construction by introducing WS-templates. This
allows us to find new lower bounds and new inequalities for weak Schur numbers. One may notice the significant gap
between the former lower bounds for weak Schur numbers obtained by conducting a computer search and the new lower bounds
obtained with WS-templates. We reckon better WS-templates with \(n \geqslant 5\) colors can be found by making different assumptions 
and using a different method (Monte-Carlo methods for instance).
